Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2018-02-09 paper.tex
Update paper.tex

The study of crop domestication has been revolutionized by the advent and application of genomic tools.
The genomes of crops and their wild relatives tell a story of give-and-take that extends well beyond the initial stages of domestication.
Likewise, population genetic theory reinforces the proclivity of wild relatives to provide advantageous, locally-adapted alleles to crops as they disperse beyond their domestication centers into new geographies with new ecological pressures and niches.

>>>>

In the same way that Darwin explored natural selection by studying domesticated species (going so far as to feature domestic pigeons as his "special group" at the beginning of his 
\emph{On the Origin of Species} \cite{darwin2009origin}), we frequently find that modern crop systems, in tandem with their extant wild relatives, offer unparalleled opportunities for the study of several evolutionary questions, including the role of adaptive introgression in dispersal and range expansion.
The advent and application of genomics tools has lead to mounting evidence which underscores the prevalence of genetic admixture between crops and wild relatives during and well beyond the initial stages of domestication.
Likewise, population genetic theory reinforces the proclivity of wild relatives to provide advantageous, locally-adpated alleles to crops as they disperse beyond their domestication centers into new geographies with new ecological pressures and niches.
Within this new conception, the process of crop range expansion is a concurrent element of domestication, rather than a distinct event subsequent to it.
%This is a revolutionary departure from the simpler model of a temporally-constrained domestication event with subsequent dispersal, and as such, offers new questions and new opportunities for investigation.
This is a revolutionary departure from the prevailing model, and as such, offers new questions and new opportunities for investigation.
These questions take on practical importance as well as theoretical.
%Understanding the histories of domestication and adaptation inform and empower efforts to develop and improve crop systems.
Understanding a crop's history of domestication in terms of selection, adaptation, and admixture empowers efforts at crop development and improvement.
As the historic role of wild relatives in the development of many crops is increasingly clarified, it is likely that we may reevaluate the importance of conservation of wild populations (in particular or in general) that harbor agronomically-valuable alleles that may be targeted by pre-breeding efforts.
These efforts may be of particular value in the face of future climate volatility and change.

As a species, domesticated crops are among our first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In this more nuanced and dynamic understanding of crop domestication, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.
\gmj{I let these final few sentences get a little more poetic than I normally would.  I think maybe I should reel them back in, or cut them.}

%The study of crop domestication has been revolutionized by the advent and application of genomic tools.
%The genomes of crops and their wild relatives tell a story of give-and-take that extends well beyond the initial stages of domestication.
%Likewise, population genetic theory reinforces the proclivity of wild relatives to provide advantageous, locally-adapted alleles to crops as they disperse beyond their domestication centers into new geographies with new ecological pressures and niches.
